Rapid cycleway prioritisation tool

### 2020-06-03 code/index.Rmd
Remove pop-up terminology

The maps contain five layers of data that overlay the basemaps.

@@

The following three layers are the central results of our analysis, representing the most promising locations for pop-up cycleways.

@@

These are the top routes for pop-up cycleways according to our analysis. 
These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. 
For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route. 
Top routes are listed in the table below the map, so you can see more information on them. 
The number of top routes selected is normally 20, with some variation by region.

>>>>

The maps contain five layers (two of which are hidden by default) that provide the results of our analysis, overlaying the basemaps.

@@

The following three layers are the central results of our analysis, representing the most promising locations for new cycleways.

@@

These are the 'top n' road sections in terms of cycling potential with 'spare space' defined above.
They may be suitable candidates for road space reallocation to create new cycleways. 
These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. 
For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route. 
Top routes are listed in the table below the map, so you can see more information on them. 
The number of top routes selected is normally 20, with some variation by region.
